### 2021-07-11 doc/thesis/chapters/implementation.tex
emphasis
impl details

@@

@@

in fixed point, close to hardware level algorithm

>>>>

The theory behind the demodulation of an FM signal is already explained in Chapter \ref{cha:SignalProcessingTheory}.
The demodulation of an FM broadcast channel specifically, is described in Section \ref{sec:demodulation-of-broadcast-fm}.
In this section however, the DSP chain is described into more detail and with more information, as it is implemented in the various methods.\\

Fig.\ref{fig:bd_dsp_detailed} displays the detailed DSP chain as a block diagram. The following list explains implementation details about the respective DSP blocks.

@@

\begin{itemize}
  \item \textbf{Data Source}\\
    Matlab is used to generate the data source file, which is used as an input to the system.
    An audio file is read and modulated as an FM channel signal.
  \item \textbf{FM Demodulator}\\
    The FM demodulator is implemented as a Baseband Delay Modulator, as described in \ref{sec:BasebandDelayDemodulator}.
  \item \textbf{De-Emphasis Filter}\\
    The above described Matlab source generation does not include an Emphasis filter.
    Thus, a de-emphasis filter is not implemented as it is not required.
  \item \textbf{Downsample}\\
    Downsampling is implemented in a simplified version, without an anti-aliasing filter.
    It is not required, because of the following explanation.
    At this point the sampling frequency is set to 960 kHz.
    The input is band-limited at 75 kHz, which is the maximum frequency in an FM channel, as explained in Section \ref{sec:FrequencySpectrumOfABroadcastFmChannel}.
    Thus, the input has an oversampling rate of 12.8, while downsampling is only performed with a factor of 8.
  \item \textbf{Filter Group Delay Compensation}\\
    FIR filters introduce a delay on the output signal, with respect to the input.
    This is due to the property of the FIR filters' linear phase response \cite{GaziOrhan2018UDSP}.
    Since phase is directly proportional to time, the term \textit{group delay} is often used.
    This delay needs to be accounted for and compensated in digital signal processing.

\end{itemize}

@@

\subsection{Emphasis and De-Emphasis}
show effects in spectrum, show how to design the filters

\subsection{Fixed Point Arithmetic}
not developed in actual fixed point, but close to hardware level algorithm
